A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-01 main.tex
Wrote on Dependent Types.

\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organization of the Paper}

@@

% Dependent Types

% Kind, Well-formed kind

% Type Equality

>>>>

\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
\blue{コードとかはボールドを使ったほうが良いかもしれない。}
\red{Suspicious senetences are colored red.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organization of the Paper}

@@

% \LLF
\LLF is a simple \red{system} of dependent types introduced in \cite{attapl}.
It is based on Edinburgh LF\cite{harper1993framework}.
Therefore, all constants and base types are declared in the signature.
The \LLF type theory generalizes simply typed lambda calculus
by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.

% Kind, Well-formed kind
In addition to ordinary typing rules like simply typed lambda calculus,
there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
Kinding rules and well-formed kinding rules are 
introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.
For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under en environment $\G$.

% Type Equality
Type equality rules are needed because the type equivalence is not obivious unlike simply typed lambda calculus.
For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
but they are not equivalent seemingly. Thus, we must define equivalence rules.
In \LLF, equivalence is expressed with a symbol of $\E$.
$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
